{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Analysis, Convergence, and Applications }

### 2024-12-22 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

\section{Preliminaries}
    Throughout, we define $F := f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex. 
    We consider optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$.
    Fix any arbitrary $y \in \RR^n$, define for all $x \in Q$: 
        \widetilde{\mathcal M}^{L^{-1}}
        (x; y) 
        &:=
        g(x) + f(y) + \langle \nabla f(y), x - y\rangle 
        + \frac{L}{2}\Vert x - y\Vert^2, 
        \mathcal M^{L^{-1}}(x; y) &:= F(x) + \frac{L}{2}\Vert x - y\Vert^2, 
    and the proximal gradient operator $T_L := [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 
    The proximal gradient operator $T_L$ admits 
        T_Ly = \argmin_x \left\lbrace
            g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
        \right\rbrace. 
    It is a single-valued mapping, and it has its domain on the entire $\RR^n$. 
    Another operator often associated with $T_L$ is the gradient mapping operator $\mathcal G_L:= L(I - T_L)$. 
    Finally, define the Bregman divergence of $f$: 
        D_f(x, y): \RR^n \times \RR^n \rightarrow \RR 
        \defeq f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
    The lemma follows explains equates between $\mathcal M(\cdot; y), \widetilde{\mathcal M}(\cdot; y)$. 
    \begin{lemma}[Proximal gradient envelope]\label{lemma:pg-envelope}
        Fix any $y \in \RR^n$, we will have for all $x \in Q$ that: 
            \widetilde{\mathcal M}^{L^{-1}}(x; y)
            \mathcal M^{L^{-1}}(x; y)- D_f(x, y) \le \mathcal M^{L^{-1}}(x; y). 
            \widetilde{\mathcal M}^{L^{-1}}(x; y) 
            g(x) + f(y) + \langle \nabla f(y), x - y\rangle + \frac{L}{2}\Vert x - y\Vert^2
            g(x) + f(x) - f(x) + f(y) 
            + \langle \nabla f(y), x - y\rangle + \frac{L}{2}\Vert x - y\Vert^2
            F(x) - D_f(x, y) + \frac{L}{2}\Vert x - y\Vert^2 
            &= \mathcal M^{L^{-1}}(x; y) - D_f(x, y). 
    \subsection{Proximal inequality}
    \begin{theorem}[Proximal inequality]\label{thm:prox-grad-ineq}
        Fix any $y\in \RR^n$, we have for all $x \in Q$: 
            F(x) - F(T_Ly) - \langle L(y - T_Ly), x - y\rangle
            - L\Vert y - T_L y\Vert^2
            - D_f(x, y)
            0. 
        When $f$ is $\mu \ge 0$ strongly convex, it implies that 
            F(x) - F(T_Ly) - \langle L(y - T_Ly), x - y\rangle
            - \frac{L}{2}\Vert y - T_L y\Vert^2
            - \frac{\mu}{2}\Vert x - y\Vert^2
            0.
        Observe that the function $\widetilde {\mathcal M}(\cdot; y)$ is $L$ strongly convex with minimizer $T_Ly$. 
        For all $x \in Q$, it has quadratic growth condition at its minimizer $T_Ly$ which gives these equivalent inequalities: 
            \widetilde{\mathcal M}^{L^{-1}}(x; y) - 
            \widetilde{\mathcal M}^{L^{-1}}(T_Ly; y)
            - 
            \frac{L}{2}\Vert x - T_Ly\Vert^2
            0
                \mathcal M^{L^{-1}}(x; y) - D_f(x, y)
            \right) - 
            \mathcal M^{L^{-1}}(T_Ly; y) 
            - 
            \frac{L}{2}\Vert x - T_Ly\Vert^2
            &\ge 0
                \mathcal M^{L^{-1}}(x; y)
                - 
                \mathcal M^{L^{-1}}(T_Ly; y)
            - 
            D_f(x, y) 
            - \frac{L}{2}\Vert x - T_Ly\Vert^2
            &\ge 0
                F(x) - F(T_Ly) 
                \frac{L}{2}\Vert x - y\Vert^2 - 
                \frac{L}{2}\Vert T_Ly - y\Vert^2
            - 
            D_f(x, y) 
            - \frac{L}{2}\Vert x - T_Ly\Vert^2
            &\ge 0
                F(x) - F(T_Ly) 
                \frac{L}{2}
                    \Vert x - T_Ly + T_Ly - y\Vert^2
                    - 
                    \Vert y - T_Ly\Vert^2
            - 
            D_f(x, y) 
            - \frac{L}{2}\Vert x - T_Ly\Vert^2
            &\ge 0
                F(x) - F(T_Ly) 
                \frac{L}{2}
                    \Vert x - T_Ly\Vert^2 + 
                    2\langle x - T_Ly, T_Ly - y\rangle
            - 
            D_f(x, y) 
            - \frac{L}{2}\Vert x - T_Ly\Vert^2
            &\ge 0
                F(x) - F(T_Ly) + \frac{L}{2}\Vert x - T_Ly\Vert^2 
                - L\langle  x - T_Ly, y - T_Ly\rangle
            - 
            D_f(x, y) 
            - \frac{L}{2}\Vert x - T_Ly\Vert^2
            &\ge 0
            F(x) - F(T_Ly)
            - \langle L(y - T_Ly), x - T_Ly\rangle
            - D_f(x, y) 
            &\ge 0. 
        The first $\implies$ comes from Lemma \ref{lemma:pg-envelope} where we had $- \widetilde{\mathcal M}^{L^{-1}}(x; y) \ge - \mathcal M^{L^{-1}}(x; y)$. 
        \todoinline{THIS THIS PART IS WRONG WRONG WRONG!}. 
        Continuing, it has: 
            F(x) - F(T_Ly) - \langle L(y - T_Ly), x - T_Ly\rangle - D_f(x, y) &\ge 0
            F(x) - F(T_Ly)
            - \langle L(y - T_Ly), x - y + y - T_Ly\rangle - D_f(x, y) 
            &\ge 0
            F(x) - F(T_Ly)
            - \langle L(y - T_Ly),x - y \rangle
            - L\Vert y - T_Ly\Vert^2
            - D_f(x, y) 
            &\ge 0
            F(x) - F(T_Ly)
            - \langle L(y - T_Ly),x - y \rangle
            - \frac{L}{2}\Vert y - T_Ly\Vert^2
            - D_f(x, y) 
            &\ge 0
            F(x) - F(T_Ly)
            - \langle L(y - T_Ly),x - y \rangle
            - \frac{L}{2}\Vert y - T_Ly\Vert^2
            - \frac{\mu}{2}\Vert x - y\Vert^2
            &\ge 0. 
        Going from the second last inequality to the last inequality, we used the fact that $f$ is strongly convex hence for all $x, y$, it's true that $D_f(x, y) \ge \mu/2 \Vert x - y\Vert^2$. 

>>>>

\section{Preliminaries}
    Throughout, we define $F := f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex. 
    We consider optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$.
    Fix any arbitrary $y \in \RR^n$, define the model functions for all $x \in Q$
    \begin{align*}
        \widetilde{\mathcal M}^{L^{-1}}
        (x; y) 
        &:=
        g(x) + f(y) + \langle \nabla f(y), x - y\rangle 
        + \frac{L}{2}\Vert x - y\Vert^2, 
        \\
        \mathcal M^{L^{-1}}(x; y) &:= F(x) + \frac{L}{2}\Vert x - y\Vert^2, 
    \end{align*}
    When $x \in \RR\setminus Q$, the model function takes $+\infty$ value. 
    Define the proximal gradient operator and gradient mapping operator:  $T_L := [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 
    The proximal gradient operator $T_L$ admits 
    \begin{align*}
        T_Ly &= \argmin_x \left\lbrace
            g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
        \right\rbrace,
        \\
        \mathcal G_L 
        &:= L(I - T_L). 
    \end{align*}
    $T_L$ is a single-valued mapping, and it has its domain on the entire $\RR^n$. 
    Finally, define the Bregman divergence of $f$: 
    \begin{align*}
        D_f(x, y): \RR^n \times \RR^n \rightarrow \RR 
        \defeq f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
    \end{align*}
    The following lemma is an important property of $\mathcal M(\cdot; y), \widetilde{\mathcal M}(\cdot; y)$. 
    \begin{lemma}[Proximal gradient envelope]\label{lemma:pg-envelope}
        Fix any $y \in \RR^n$, we will have for all $x \in \RR$ that: 
        \begin{align*}
            \widetilde{\mathcal M}^{L^{-1}}(x; y)
            &= 
            \mathcal M^{L^{-1}}(x; y)- D_f(x, y) \le \mathcal M^{L^{-1}}(x; y). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        Consider any $x \in Q$, by definition it has: 
        \begin{align*}
            \widetilde{\mathcal M}^{L^{-1}}(x; y) 
            &= 
            g(x) + f(y) + \langle \nabla f(y), x - y\rangle + \frac{L}{2}\Vert x - y\Vert^2
            \\
            &= 
            g(x) + f(x) - f(x) + f(y) 
            + \langle \nabla f(y), x - y\rangle + \frac{L}{2}\Vert x - y\Vert^2
            \\
            &= 
            F(x) - D_f(x, y) + \frac{L}{2}\Vert x - y\Vert^2 
            \\
            &= \mathcal M^{L^{-1}}(x; y) - D_f(x, y). 
        \end{align*}
        The equality is trivially true when $x \in \RR \setminus Q$. 
    \end{proof}
    \subsection{Proximal inequality}
    \begin{theorem}[Proximal inequality]\label{thm:prox-grad-ineq}
        Fix any $y\in \RR^n$, we have for all $x \in \RR^n$: 
        \begin{align*}
            F(x) - F(T_Ly) - \langle L(y - T_Ly), x - y\rangle
            - L\Vert y - T_L y\Vert^2
            - D_f(x, y)
            &\ge  
            0. 
        \end{align*}
        Recall that $f$ is $\mu \ge 0$ strongly convex and $L$ Lipschitz smooth, hence the following is implied: 
        \begin{align*}
            F(x) - F(T_Ly) - \langle L(y - T_Ly), x - y\rangle
            - \frac{L}{2}\Vert y - T_L y\Vert^2
            - \frac{\mu}{2}\Vert x - y\Vert^2
            &\ge  
            0.
        \end{align*}
    \end{theorem}
    \begin{proof}
        For lighter notations in this proof, we use $\mathcal M(\cdot, y), \widetilde{\mathcal M}(\cdot, y)$ instead of $\mathcal M^{L^{-1}}(\cdot, y), \widetilde{\mathcal M}^{L^{-1}}(\cdot, y)$. 
        And we denote $T$ for the proximal gradient operator instead of $T_L$. 
        We can do this because the Lipschitz constant $L$ is fixed throughout the proof hence it can be omitted.

        % Observe that the function $\widetilde {\mathcal M}(\cdot; y)$ is $L$ strongly convex with minimizer $T_Ly$. 
        % For all $x \in Q$, it has quadratic growth condition at its minimizer $T_Ly$ which gives these equivalent inequalities: 
        % {\small
        %     \widetilde{\mathcal M}^{L^{-1}}(x; y) - 
        %     \widetilde{\mathcal M}^{L^{-1}}(T_Ly; y)
        %     - 
        %     \frac{L}{2}\Vert x - T_Ly\Vert^2
        %     &\ge 
        %     0
        %     \\
        %     \implies
        %     \left(
        %         \mathcal M^{L^{-1}}(x; y) - D_f(x, y)
        %     \right) - 
        %     \mathcal M^{L^{-1}}(T_Ly; y) 
        %     - 
        %     \frac{L}{2}\Vert x - T_Ly\Vert^2
        %     &\ge 0
        %     \\
        %     \iff 
        %     \left(
        %         \mathcal M^{L^{-1}}(x; y)
        %         - 
        %         \mathcal M^{L^{-1}}(T_Ly; y)
        %     \right)
        %     - 
        %     D_f(x, y) 
        %     - \frac{L}{2}\Vert x - T_Ly\Vert^2
        %     &\ge 0
        %     \\
        %     \iff 
        %     \left(
        %         F(x) - F(T_Ly) 
        %         + 
        %         \frac{L}{2}\Vert x - y\Vert^2 - 
        %         \frac{L}{2}\Vert T_Ly - y\Vert^2
        %     \right)
        %     - 
        %     D_f(x, y) 
        %     - \frac{L}{2}\Vert x - T_Ly\Vert^2
        %     &\ge 0
        %     \\
        %     \iff 
        %     \left(
        %         F(x) - F(T_Ly) 
        %         + 
        %         \frac{L}{2}
        %         \left(
        %             \Vert x - T_Ly + T_Ly - y\Vert^2
        %             - 
        %             \Vert y - T_Ly\Vert^2
        %         \right)
        %     \right)
        %     - 
        %     D_f(x, y) 
        %     - \frac{L}{2}\Vert x - T_Ly\Vert^2
        %     &\ge 0
        %     \\
        %     \iff 
        %     \left(
        %         F(x) - F(T_Ly) 
        %         + 
        %         \frac{L}{2}
        %         \left(
        %             \Vert x - T_Ly\Vert^2 + 
        %             2\langle x - T_Ly, T_Ly - y\rangle
        %         \right)
        %     \right)
        %     - 
        %     D_f(x, y) 
        %     - \frac{L}{2}\Vert x - T_Ly\Vert^2
        %     &\ge 0
        %     \\
        %     \iff
        %     \left(
        %         F(x) - F(T_Ly) + \frac{L}{2}\Vert x - T_Ly\Vert^2 
        %         - L\langle  x - T_Ly, y - T_Ly\rangle
        %     \right)
        %     - 
        %     D_f(x, y) 
        %     - \frac{L}{2}\Vert x - T_Ly\Vert^2
        %     &\ge 0
        %     \\
        %     \iff 
        %     F(x) - F(T_Ly)
        %     - \langle L(y - T_Ly), x - T_Ly\rangle
        %     - D_f(x, y) 
        %     &\ge 0. 
        % }
        % The first $\implies$ comes from Lemma \ref{lemma:pg-envelope} where we had $- \widetilde{\mathcal M}^{L^{-1}}(x; y) \ge - \mathcal M^{L^{-1}}(x; y)$. 
        % \todoinline{THIS THIS PART IS WRONG WRONG WRONG!}. 
        % Continuing, it has: 
        %     F(x) - F(T_Ly) - \langle L(y - T_Ly), x - T_Ly\rangle - D_f(x, y) &\ge 0
        %     \\
        %     \iff
        %     F(x) - F(T_Ly)
        %     - \langle L(y - T_Ly), x - y + y - T_Ly\rangle - D_f(x, y) 
        %     &\ge 0
        %     \\
        %     \iff
        %     F(x) - F(T_Ly)
        %     - \langle L(y - T_Ly),x - y \rangle
        %     - L\Vert y - T_Ly\Vert^2
        %     - D_f(x, y) 
        %     &\ge 0
        %     \\
        %     \implies 
        %     F(x) - F(T_Ly)
        %     - \langle L(y - T_Ly),x - y \rangle
        %     - \frac{L}{2}\Vert y - T_Ly\Vert^2
        %     - D_f(x, y) 
        %     &\ge 0
        %     \\
        %     \implies
        %     F(x) - F(T_Ly)
        %     - \langle L(y - T_Ly),x - y \rangle
        %     - \frac{L}{2}\Vert y - T_Ly\Vert^2
        %     - \frac{\mu}{2}\Vert x - y\Vert^2
        %     &\ge 0. 
        % Going from the second last inequality to the last inequality, we used the fact that $f$ is strongly convex hence for all $x, y$, it's true that $D_f(x, y) \ge \mu/2 \Vert x - y\Vert^2$.

### 2024-12-22 Notebook LaTEX/Proposal/main.tex
>w<, changes

\section{Preliminaries}
    Beck's book \cite{beck_first-order_2017}. 
    \subsection{Fundamentals in convex analysis}
    \subsection{Fundamentals in non-convex analysis}

>>>>

\section{Preliminaries}
    \todoinline{
        Assumptions: Additive composite type convex objective until specified.  
    }
    \subsection{Fundamentals in convex analysis}
        \todoinline{
            Definitions: 
            \begin{enumerate}
                \item The proximal gradient operator. 
                \item The proximal mapping operator. 
                \item The Bregman Divergence of function. 
                \item Strong convexity. 
            \end{enumerate}
            Lemma: 
            \begin{enumerate}
                \item Quadratic growth conditions of a strongly convex function. 
            \end{enumerate}
            Theorems: 
            \begin{enumerate}
                \item The proximal gradient inequality, for additive composite objective where the smooth part is $\mu \ge 0$ strongly convex. 
            \end{enumerate}
        }
    \subsection{Fundamentals in non-convex analysis}
